Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-02-13 Report/decomposition_solutions.tex
halfcooked

Now, to decouple the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which include all interference terms relevant for the transmission of \ac{BS} \me{b}, can either be fixed or treated as a variable in each iteration in accordance to the decomposition method. Since the \ac{BS} specific precoders are solved independently, we assume local channel information and queues are available at each \ac{BS} \me{b_k} together with the cross channel knowledge \me{\mvec{H}{b_k,k,n}, \forall k\in \bar{\mc{U}}_{b_k}} through uplink sounding and the receive beamformers \me{\mvec{w}{l,k,n}}.

>>>>

Now, to decouple the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which include all interference terms relevant for the transmission of \ac{BS} \me{b}, can either be fixed or treated as a variable in each iteration in accordance to the decomposition method. Since the \ac{BS} specific precoders are solved independently, we assume local channel information and queues are available at each \ac{BS} \me{b_k} together with the cross channel knowledge \me{\mvec{H}{b_k,k,n}, \forall k\in \bar{\mc{U}}_{b_k}} through precoded uplink sounding using the receive beamformers \me{\mvec{w}{l,k,n}} \cite{komulainen2013effective}.

### 2015-02-13 Report/introduction.tex
halfcooked

In general, the resource allocation problems are formulated by assigning a binary variable for each user to indicate the presence or the absence in a particular resource \cite{admission_control}. \review{In contrast, the linear transmit precoders, which are complex vectors, are implicitly used as decision variables, thereby avoiding the explicit modeling of binary decision variables. It solves two purposes. First, the formulation determines the transmission rate on a certain resource, and, secondly, by making the transmit beamformer of a particular user to be a zero vector, the corresponding user will not be scheduled on a certain resource. In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergence}.

>>>>

In general, the resource allocation problems are formulated by assigning a binary variable for each user to indicate the presence or the absence in a particular resource \cite{admission_control}. \review{In contrast, the linear transmit precoders, which are complex vectors, are implicitly used as decision variables, thereby avoiding the explicit modeling of binary decision variables. It is used to determine the transmission rate of a user on a space-frequency resource if the precoder vector is non-zero. A zero transmit precoder indicates the absence of the user on a given resource. In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergence}.

### 2015-02-13 Report/kkt_mse_approach.tex
halfcooked

In this section, we discuss an alternative way to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}. In contrast to Section \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations. The proposed methods in this section provide algorithms that can be of practical importance owing to the limited signaling requirements. \review{We consider an idealistic assumption of a \ac{TDD} system due to the knowledge of complete channel information at the transmitter}.  Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}. Since the formulation in \cite{kaleva2013decentralized,kaleva2013primal} are similar to the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, it requires explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.

@@

With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
\iftoggle{single_column}{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \eqspace \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
	\text{subject to} & \nonumber \\
	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise \nonumber \\
	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.

@@

When the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative and due to the projection operator \me{[x]^+} in \eqref{kkt-mse-4.2}, it will be zero, thereby forcing \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}} as in \eqref{kkt-mse-4.1}. Once the \me{\alpha_k^{(i)}} is reduced, the precoder weight in \eqref{kkt-mse-4.3} is lowered to make the rate \me{t_k^{(i)} < t_k^{(i-1)}} eventually. \review{Since \me{\rho} depend on the system size, we fix the value of \me{\rho = 0.1} in our simulations irrespective of the system, which affects the convergence behavior marginally.}

@@

\review{The Algorithm \ref{algo-4} outlines a practical way of implementing the transmit precoders in a distributed manner using \ac{OTA} signaling of the transmit precoders and the receive beamformers for certain iterations before the actual transmission of data is performed with it. Unlike \ac{PD} or \ac{ADMM} approach, all variables are updated at once, \textit{i.e}, the \ac{SCA} point of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable \me{\alpha} using subgradient update, it is not guaranteed to obtain the same point as that of the centralized problem. Since the problem solution in \eqref{kkt-mse-4} is equivalent to the centralized formulation in \eqref{eqn-mse-2} if the receive beamformers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed and optimized for the transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}, the problem is guaranteed to converge to the centralized solution. Note that it requires four iterations to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, dual variable update loop and the bisection method for finding the transmit precoders. In order to avoid this, the proposed method performs the group update of all variables to obtain the transmit and the receive beamformers with the limited number of iterations. If the step size \me{\rho < 1}, the algorithm for \me{\ell_2} norm will converge by using the arguments for controlling overallocation problem and the nonincreasing objective function, since the earlier iterates are in fact the operating point for the current iteration.}

>>>>

In this section, we discuss an alternative way to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}. In contrast to Section \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations. The proposed methods in this section provide algorithms that can be of practical importance owing to the limited signaling requirements. \review{We consider an idealized \ac{TDD} system due to the knowledge of complete channel information at the transmitter}.  Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}. Since the formulation in \cite{kaleva2013decentralized,kaleva2013primal} are similar to the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, it requires explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.

@@

With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
\iftoggle{single_column}{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \eqspace \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
%\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}{
\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
	\text{subject to} & \nonumber \\
	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise \nonumber \\
	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
\end{IEEEeqnarray}
}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.

@@

When the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative and due to the projection operator \me{[x]^+} in \eqref{kkt-mse-4.2}, it will be zero, thereby forcing \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}} as in \eqref{kkt-mse-4.1}. Once the \me{\alpha_k^{(i)}} is reduced, the precoder weight in \eqref{kkt-mse-4.3} is lowered to make the rate \me{t_k^{(i)} < t_k^{(i-1)}} eventually. \review{The choice of \me{\rho} is susceptible to the system model under consideration, which affects the convergence speed of the iterative algorithm. In our simulations, we fixed \me{\rho = 0.1} irrespective of the model under consideration.}

@@

\review{The Algorithm \ref{algo-4} outlines a practical way of implementing the transmit precoders in a distributed manner using \ac{OTA} signaling of the transmit precoders and the receive beamformers for certain iterations before the actual transmission of data is performed with it. Unlike \ac{PD} or \ac{ADMM} approach, all variables are updated at once, \textit{i.e}, the \ac{SCA} point of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable \me{\alpha} using subgradient update, it is not guaranteed to obtain the same point as that of the centralized problem. Since the problem solution in \eqref{kkt-mse-4} is equivalent to the centralized formulation in \eqref{eqn-mse-2} if the receive beamformers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed and optimized for the transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}, the problem is guaranteed to converge to the centralized solution. Note that it requires four iterations to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, dual variable update loop and the bisection method for finding the transmit precoders. In order to avoid this, the proposed method performs the group update of all variables to obtain the transmit and the receive beamformers with the limited number of iterations. If the step size \me{\rho < 1}, the algorithm for \me{\ell_2} norm will converge by using the arguments on controlling overallocation and the nonincreasing objective function, since the earlier iterates are the operating point for the current iteration.}

### 2015-02-13 Report/problem_formulation.tex
halfcooked

The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by limiting it to a constant value. \review{In fact, using \me{\ell_{q=2}} in \eqref{eqn-4.2}, we obtain the following objective
\begin{equation}\label{pf-1}
\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2,
\end{equation}
which is equivalent to the objective defined in \eqref{q_gen_sum}. Note that the equivalence can be seen either by discarding \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is significantly greater than the maximum allowable transmission.}

>>>>

The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by limiting it to a constant value. \review{In fact, using \me{\ell_{q=2}} in \eqref{eqn-4.2}, we obtain the following objective
\begin{equation}\label{pf-1}
\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2,
\end{equation}
which is similar to the objective in \eqref{q_gen_sum}. Note that the equivalence can be seen either by removing \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is significantly large for all users such that \me{t_k^2} has no impact on the objective function.}

### 2015-02-13 Report/sub_channel_wsrm.tex
halfcooked

The complexity of the \ac{JSFRA} algorithm scales with the number of sub-channels considered. In addition, the iterations required for the algorithm convergence increases with the problem size. To overcome the complexity, we can adopt the distributed approaches presented in \cite{palomar2006tutorial,boyd2011distributed} for sub-channel wise precoder design using primal or dual decomposition.

As an alternative sub-optimal solution, we present \acl{QM} \ac{SRA}, which designs the precoders independently across the sub-channels in a sequential manner using the unserviced  number of packets after each sub-channel allocation. The \ac{BS} transmit power is fixed across the sub-channel \me{n} as \me{P_{\max,n}}. The power sharing can be equal or based on predetermined pattern as in partial frequency reuse across the sub-channels. After fixing the power and the backlogged packets for a sub-channel \me{i}, precoders are determined using the \ac{JSFRA} algorithm presented in Section \ref{sec-3.2.1} or \ref{sec-3.3} for each sub-channel in a sequential manner. Once the precoders and the corresponding rates are identified, the unserviced backlogged packets for the next sub-channel \me{i+1} is updated for user \me{k} as
\begin{equation}	\label{eqn-weight}
	Q_{k,i+1} = \max{\left \lbrace Q_k - \sum_{j = 1}^{i} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \right \rbrace }, \; \forall \; k \in \mathcal{U},
\end{equation}
where \me{t_{l,k,j}} denotes the rate corresponding to the user \me{k} on the \me{\ith{j}} sub-channel and \me{\ith{l}} spatial stream and the initial values are given as \me{Q_{k,1} = Q_k, \forall k}. Note that the proposed scheme is sensitive to the order of the sub-channel selection due to the sequential precoder design for each sub-channel. However, the \ac{SRA} approach provides faster convergence in contrast to the \ac{JSFRA} formulation due to the substantial reduction in the optimization variables for each sub-channel problem. 
As the number of user increases, the \ac{SRA} formulation will be insusceptible to the sub-channel ordering due to the channel hardening and the availability of users with all possible channel vectors.
%The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}
%\begin{algorithm}
% \SetAlgoLined
% \DontPrintSemicolon
% \BlankLine
% \SetKwInput{KwInit}{Initialize}
% \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}}}
% \KwIn{permute \me{\mathcal{N} \rightarrow \tilde{\mathcal{N}}}}
% \For{\me{n \leftarrow 1 } \KwTo \me{N}}{
% update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{N}}(n)}\;
% \KwOut{\me{\mvec{m}{l,k,\hat{n}}} and \me{\mvec{w}{l,k,\hat{n}} \fall l \in \set{1,2,\dotsc,L}}}
% \KwInit{\me{i=0} and \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
% update \me{\mvec{w}{l,k,\hat{n}}} and \me{\tilde{\mbf{u}}_{l,k,\hat{n}}} using \eqref{eqn-10} and \eqref{eqn-8}\;
% \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
% initialize \me{j = 0}\;
% \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
% solve for \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} with per sub-channel power constraint \me{P_{\max,\hat{n}}}\;
% update the constraint set \eqref{eqn-8} with \me{\tilde{u}_{l,k,\hat{n}}} and \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-wsrm-expr}\;
% $j = j + 1$\;
% }
% update \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
% $i = i + 1$\;
% }
% }
% \caption{Algorithm of \acs{SRA} scheme}
% \label{algo-5}
%\end{algorithm}
%

>>>>

The complexity of the \ac{JSFRA} algorithm scales with the number of sub-channels considered. In addition, the iterations required for the algorithm convergence increases with the problem size. To overcome the complexity, we can decouple the problem to sub-channel specific subproblems by using distributed approaches presented in \cite{palomar2006tutorial,boyd2011distributed} to design the precoders using primal or dual decomposition.

As an alternative sub-optimal solution, we present \acl{QM} \ac{SRA}, which solves for the precoders using \ac{JSFRA} formulation only for a specific sub-channel \me{i} with a fixed transmit power \me{P_{\max,i}}. The sharing of power can be equal or based on a predetermined pattern as in partial frequency reuse for the sub-channels by adhering to 
\begin{equation}
\sum_{i=1}^N P_{\max,i} = P_{\max}.
\end{equation}
Even though \me{N} sub-channels are present at any given scheduling instant, precoders are solved for each sub-channel in a sequential manner with the sub-channel specific total power constraint \me{P_{\max,i}} and the backlogged packets. Let \me{Q_{k,i}} number of backlogged packets associated with user \me{k} before solving for precoders specific to the sub-channel \me{i}. Since the precoder design is sequential, for the initial sub-channel, the number of backlogged packets is given by \me{Q_{k,1} = Q_k} and for the consecutive sub-channels, it is given by
\begin{equation}	\label{eqn-weight}
	Q_{k,i+1} = \max{\left \lbrace Q_k - \sum_{j = 1}^{i} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \right \rbrace }, \; \forall \; k \in \mathcal{U},
\end{equation}
where \me{t_{l,k,j}} denotes the rate corresponding to the user \me{k} on the \me{\ith{j}} sub-channel and \me{\ith{l}} spatial stream. Note that the proposed scheme is sensitive to the order of the sub-channel selection due to the sequential precoder design for each sub-channel. However, the \ac{SRA} approach provides faster convergence in contrast to the \ac{JSFRA} formulation due to the substantial reduction in the optimization variables for each sub-channel problem. As the number of user increases, the \ac{SRA} formulation will be insusceptible to the sub-channel ordering due to the multi-user diversity.
%The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}
%\begin{algorithm}
% \SetAlgoLined
% \DontPrintSemicolon
% \BlankLine
% \SetKwInput{KwInit}{Initialize}
% \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}}}
% \KwIn{permute \me{\mathcal{N} \rightarrow \tilde{\mathcal{N}}}}
% \For{\me{n \leftarrow 1 } \KwTo \me{N}}{
% update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{N}}(n)}\;
% \KwOut{\me{\mvec{m}{l,k,\hat{n}}} and \me{\mvec{w}{l,k,\hat{n}} \fall l \in \set{1,2,\dotsc,L}}}
% \KwInit{\me{i=0} and \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
% update \me{\mvec{w}{l,k,\hat{n}}} and \me{\tilde{\mbf{u}}_{l,k,\hat{n}}} using \eqref{eqn-10} and \eqref{eqn-8}\;
% \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
% initialize \me{j = 0}\;
% \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
% solve for \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} with per sub-channel power constraint \me{P_{\max,\hat{n}}}\;
% update the constraint set \eqref{eqn-8} with \me{\tilde{u}_{l,k,\hat{n}}} and \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-wsrm-expr}\;
% $j = j + 1$\;
% }
% update \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
% $i = i + 1$\;
% }
% }
% \caption{Algorithm of \acs{SRA} scheme}
% \label{algo-5}
%\end{algorithm}
%
